Gait Segmentation Model for Rotation Time Series Collected by a Wearable Sensor using Machine Learning

### 2025-01-27 article_segmentation.qmd
Generate table 1 via gt as latex code cells do not render in html.

```{=latex}
\begin{longtable}{|p{2cm}|p{2cm}|p{2cm}|p{6cm}|}
\hline
    ID & Gender  & Age & Walking speed (cm/s) \\
    \hhline{=:=:=:=}
    MBA & M  & 50-60 &  \vspace{-0.2cm} \begin{itemize}[itemsep=0mm,, leftmargin=1mm]
                        \item[-] Slow: 60
                        \item[-] Intermediate: 116 
                        \item[-] Preferential: 145
                        \item[-] Fast: 199
                       \end{itemize} \\ 
    \hline
    MBO & F  & 20-30 &  \vspace{-0.2cm} \begin{itemize}[itemsep=0mm,, leftmargin=1mm]
                        \item[-] Slow: 73
                        \item[-] Intermediate: 122
                        \item[-] Preferential: 145
                        \item[-] Fast: 188
                       \end{itemize} \\ 
    \hline
    MSI & F  & 20-30 &  \vspace{-0.2cm} \begin{itemize}[itemsep=0mm,, leftmargin=1mm]
                        \item[-] Slow: 67
                        \item[-] Intermediate: 115
                        \item[-] Preferential: 148
                        \item[-] Fast: 179
                       \end{itemize} \\ 
    \hline
    MTR & M  & 20-30 &  \vspace{-0.2cm} \begin{itemize}[itemsep=0mm,, leftmargin=1mm]
                        \item[-] Slow: 77
                        \item[-] Preferential: 132
                        \item[-] Fast: 185
                       \end{itemize} \\ 
    \hline
    NNE & F  & 20-30 &  \vspace{-0.2cm} \begin{itemize}[itemsep=0mm,, leftmargin=1mm]
                        \item[-] Slow: 57
                        \item[-] Intermediate: 116 
                        \item[-] Preferential: 147
                        \item[-] Fast: 190
                       \end{itemize} \\ 
    \hline
    TDE & M  & 50-60 &  \vspace{-0.2cm} \begin{itemize}[itemsep=0mm,, leftmargin=1mm]
                        \item[-] Slow: 61
                        \item[-] Preferential: 120
                        \item[-] Fast: 193
                       \end{itemize} \\ 
    \hline
\end{longtable}
```

>>>>

```{r}
data.frame(
  id = c("MBA", "MBO", "MSI", "MTR", "NNE", "TDE"),
  gender = c("M", "F", "F", "M", "F", "M"),
  age = c("50-60", "20-30", "20-30", "20-30", "20-30", "50-60"),
  slow = c(60, 73, 67, 77, 57, 61),
  intermediate = c(116, 122, 115, NA, 116, NA),
  preferential = c(145, 145, 148, 132, 147, 120),
  fast = c(199, 188, 179, 185, 190, 193)
) |> 
  gt::gt() |> 
  gt::tab_spanner(
    label = "Walking speed (cm/s)",
    columns = c(slow, intermediate, preferential, fast)
  ) |> 
  gt::cols_label(
    id = "ID",
    gender = "Gender",
    age = "Age range (years)",
    slow = "Slow",
    intermediate = "Intermediate",
    preferential = "Preferential",
    fast = "Fast"
  ) |> 
  gt::sub_missing() |> 
  gt::opt_stylize(style = 6, color = 'gray') |> 
  gt::tab_options(
    column_lab
  )
```
